\paragraph{}
Praise be to ALLAH, his Majesty for his uncountable blessings, and best prayers and peace be unto his best messenger Mohammed, his pure descendant, and his family and his noble companions.
\paragraph{}
First I would deeply love to thank my family. Starting, with my beloved parents, mama Saida and papa Benali. My lovely Sisters Sabrine Amira Youssra and Nermine. My Unique Brothers Yacine and  Aimen and my loving aunties Cheikh Houria and Kacem Abdia. Without their support and love throughout the years, I wouldn't be where I am today. They have always been there for me and I will always love them and be thankful to have them. 
\paragraph{}
Distinct appreciation goes to my supervisor, Dr. Hamadi Abdelkader, for his supervision and constant support. for always being there to help, even at late hours, even when he has tons of things to do. His invaluable help of constructive comments, encouragement, and suggestions throughout the experimental and thesis works have contributed to the success of this research.
\paragraph{}
Not forgotten, my appreciation to Dr. Filali Fatima Zohra, for providing us with help to access cloud resources which without it the experiments may be impossible to realize. And for Dr. Karim Sehaba for his advice on how to structure a thesis. 
\paragraph{}
My acknowledgment also goes to all professors and staffs of the University of Mostaganem that helped me or made the university a good place to be for me especially Mr. Houari Benmekki, Mr. Besnassi Miloud, Mr. Menad Si Mohamed Bekkai, Mr.Bessaoud Karim, Mrs. Hocine Nadia, Mrs. M.Abid, Mr. Mohamed Amine Benmalti, and Mrs. Hamami Dalila.
\paragraph{}
Sincere thanks and appreciation to all friends whose support played a significant role in keeping me motivated especially Wahab Dichou, Mohamed Ameur, Mohamed Bensaadallah, Nour El houda Larbi, Ilhem Derdour, Meriem Benyahia, Houcine Zaidi, Wassini Ikkache, Youness Ikkache. their friendship is priceless.
\paragraph{}
My gratitude goes also to Scandiweb Company for using their laptop. I would love to infinitely thank StackOverflow and the opensource community for making the world easier for me.
\paragraph{}
Last but not least, I would thank all of those who supported me with a word, a gesture, or a thought. 