\paragraph{}
Tuberculosis is a chronic infectious disease caused by a bacterium. called " Mycobacterium Tuberculosis" or Bacillus Koch (\ac{bk}). Its most current and most common form (85\% of cases) is pulmonary tuberculosis, but there are also extra-pulmonary forms such as bone tuberculosis, ganglion tuberculosis and renal tuberculosis.
\paragraph{}
Tuberculosis can develop rapidly after the first contact with the microbe, but it can also appear several years later.
\section{Latent \ac{tb} infection (\ac{ltbi})}
\paragraph{}
\ac{ltbi} is the presence of tubercle bacilli within the body without manifestation of the disease. \ac{ltbi} carriers are by definition non-contagious and pose no risk to those around them.
\section{Active tuberculosis}
\paragraph{}
Active tuberculosis is a condition in which the body’s immune system is unable to fight off or defend against the Mycobacterium tuberculosis bacterium. This inability causes an infection of the lungs, which is the most common presentation, or other parts of the body (tuberculosis is a multisystemic disease). Apart from the respiratory system, the organ systems most commonly affected include the gastrointestinal systemT, the musculoskeletal system, the lymphoreticular system, and the reproductive system, as well as the skin and the liver.
\paragraph{}
Globally, the best estimate is that 10.0 million people (range, 9.0–11.1 million) developed \ac{tb} disease in 2017: 5.8 million men, 3.2 million women and 1.0 million children \cite{TBT:3}. There were cases in all countries and age groups, but overall 90\% were adults (aged ≥15 years), 9\% were people living with \ac{hiv} (72\% in Africa) and two thirds were in eight countries: India (27\%), China (9\%), Indonesia (8\%), the Philippines (6\%), Pakistan (5\%), Nigeria (4\%), Bangladesh (4\%) and South Africa (3\%). These and 22 other countries in \ac{who}’s list of 30 high \ac{tb} burden countries accounted for 87\% of the world’s cases\cite{TBT:3}.4 Only 6\% of global cases were in the \ac{who} European Region (3\%) and \ac{who} Region of the Americas (3\%)\cite{TBT:3}. 